\papertitle

### 2014-03-17 final-report/paper.tex
Little fixes, added outlook

We propose a visualization system for understanding and exploring query execution and data movement in a distributed database management system (DDBMS). Our tool will provide insight into: (1) data flow between query fragments and between workers, (2) query execution and operator dependencies, (3) cluster utilization, (4) network utilization. Our tool, which we call \system, will help developers understand and improve query execution, and will provide insight into common problems such as data skew or performance bottlenecks.

@@

There are two possible approaches that we explored to collect event logs that can be used to extract spans and other performance related data necessary for the visualization. First, events could be logged to files using a standard logging tool and then collect the files on one node using remote copy. Once the logs are in one place, they can be parsed and the data transformed into the desired format.

@@

\begin{figure}[ht]
  \includegraphics[width=\columnwidth]{viz_arch}
  \caption{Architecture}
  \label{fig:arch}
\end{figure}

@@

\subsection{Front-end}
The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3 to delive an interactive visualization experience to the user. D3 is a JavaScript framework for data visualziation on the web. We used visualization techniques such as \emph{focus+context} that possible to implement conveniently using D3.

@@

% Dom

>>>>

We propose a visualization system for understanding and exploring query execution and data movement in a distributed database management system (DDBMS). Our tool provides insight into: (1) data flow between query fragments and between workers, (2) query execution and operator dependencies, (3) cluster utilization, (4) network utilization. Our tool, which we call \system, helps developers understand and improve query execution, and provides insight into common problems such as data skew or performance bottlenecks.

@@

There are two possible approaches that we explored to collect event logs that can be used to extract spans and other performance related data necessary for the visualization. First, events could be logged to files using a standard logging tool and then collect the files on one node using remote copy. Once the logs are on one machine, the logs can be parsed and the data can be transformed into the desired format.

@@

\begin{figure}[ht]
  \includegraphics[width=\columnwidth]{viz_arch}
  \caption{Overview of the log collection and transformation architecture. Raw event logs are collected on each worker. The data is stored in relations. To download the data, a query has to be executed.}
  \label{fig:arch}
\end{figure}

@@

\subsection{Front-end}

The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3 to delive an interactive visualization experience to the user. D3 is a JavaScript framework for data visualziation on the web. We used visualization techniques such as \emph{focus+context} that possible to implement conveniently using D3.

@@

A focus of the current implementation is on scalability to many workers and long running queries. More aggregations have to be done by the database itself. Most importantly, in the fragment visualization that shows spans for all events we should limit the data that is being downloaded and rendered to what the user can see. With the architecture as explained in Section~\ref{sec:back}, we are able to express these filter conditions as queries.
